Parameters estimation via HOSVD

### 2024-12-23 Code/R/Research/HOSVD parameters estimate.Rmd
Part-way signal extraction plots

@@

# no rates
rates.true <- c(0, 0)
# both rates -0.01
# rates.true <- c(-0.01, -0.01)
# both rates -0.02
# rates.true <- c(-0.02, -0.02)
# rates from paper
# rates.true <- c(-0.01, -0.02)

@@

    rec.ssa.rmse[j] <- mse.ssa |> mean() |> sqrt()
}

min.ssa.rmse <- c(min(rec.ssa.rmse), Ls[which.min(rec.ssa.rmse)])

## Графики RMSE
```{r}
rec1.df <- rec.rmse |> as.data.frame() |>
  mutate(dims = factor(x = apply(tens.dims, 1, paste, collapse = "x"),
                       levels = apply(tens.dims, 1, paste, collapse = "x"))) |>
  pivot_longer(!dims, names_to = "trunc dims", names_prefix = "V", values_to = "RMSE") |>
  mutate(`trunc dims` = as.factor(paste(trunc_dims[as.integer(`trunc dims`)])))

rec1.plot <- rec1.df |> ggplot() +
  geom_line(aes(
    x = dims,
    y = RMSE,
    group = `trunc dims`,
    colour = `trunc dims`,
    linetype = `trunc dims`
  ), lwd = 1.2) + 
  geom_abline(slope = 0, intercept = min.ssa.rmse[1], col = "gray10", lty = 3) +
  annotate(geom = "text", x = 5, y = min.ssa.rmse[1] * 1.02, label = "SSA min RMSE") +
  ylim(min.ssa.rmse[1], 0.0245) + 
  theme(axis.text.x = element_text(angle = 90))

plot.save(
  rec1.plot,
  paste0("./img/rec_dim_rmse", plot.name, ".pdf"),
  pdf,
  width = 9,
  height = 6,
  save = save
)
```

>>>>

save(rec.rmse, file = paste0("./Research/comp_results/signal", plot.name, "_hossa.RData"))
close(pb)
```

@@

@@

    rec.ssa.rmse[j] <- mse.ssa |> mean() |> sqrt()
}
close(pb)

save(rec.ssa.rmse, file = paste0("./Research/comp_results/signal", plot.name, "_ssa.RData"))
min.ssa.rmse <- c(min(rec.ssa.rmse), Ls[which.min(rec.ssa.rmse)])
```

## Графики RMSE
```{r}
pltnms <- c("_no_rates", "_small_eq_rates", "_large_eq_rates", "")
pn <- 1

load(file = paste0("./Research/comp_results/signal", pltnms[pn], "_hossa.RData"))
load(file = paste0("./Research/comp_results/signal", pltnms[pn], "_ssa.RData"))
```

```{r}
rec.df <- rec.rmse |> as.data.frame() |>
  mutate(dims = factor(x = apply(tens.dims, 1, paste, collapse = "x"),
                       levels = apply(tens.dims, 1, paste, collapse = "x"))) |>
  pivot_longer(!dims, names_to = "trunc dims", names_prefix = "V", values_to = "RMSE") |>
  mutate(`trunc dims` = as.factor(paste(trunc_dims[as.integer(`trunc dims`)])))

rec.plot <- rec.df |> ggplot() +
  geom_line(aes(
    x = dims,
    y = RMSE,
    group = `trunc dims`,
    colour = `trunc dims`,
    linetype = `trunc dims`
  ), lwd = 1.2) + 
  geom_abline(slope = 0, intercept = min.ssa.rmse[1], col = "gray10", lty = 3) +
  annotate(geom = "text", x = 5, y = min.ssa.rmse[1] * 1.02, label = "SSA min RMSE") +
  ylim(min.ssa.rmse[1], 0.0245) + 
  theme(axis.text.x = element_text(angle = 90))

plot.save(
  rec.plot,
  paste0("./img/rec_dim_rmse", plot.name, ".pdf"),
  pdf,
  width = 9,
  height = 6,
  save = save
)
```
